\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
is written to disk -> can be written to disk

%%%%%%%%%%%%%%%%%  Internal data representation
The internal data representation closely follows the structure of GDML. A \verb|Registry| class aggregates Python ordered dictionaries that are  used to store the main 
elements of a GDML file. As a \PYGEOMETRY{} user instantiates the geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry 
is written to disk as a GDML file.\verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.

>>>>

%%%%%%%%%%%%%%%%%  Internal data representation
The internal data representation closely follows the structure of GDML. A \verb|Registry| class aggregates Python ordered dictionaries that are  used to store the main 
elements of a GDML file. As a \PYGEOMETRY{} user instantiates the geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry 
can be written to disk as a GDML file. \verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
